### 2022-08-15 manuscript.Rmd
Update title page

author: 
  - name          : "Alexander Enge"
    affiliation   : "1,2"
    corresponding : "yes"
    address       : "Rudower Chaussee 18, 12489 Berlin, Germany"
    email         : "alexander.enge@hu-berlin.de"
  - name          : "Franziska Süß"
    affiliation   : "3"
  - name          : "Rasha Abdel Rahman"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin, Germany"
  - id            : "2"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig, Germany"
  - id            : "3"
    institution   : "Fachhochschule des Mittelstands, Minna-Neuburger-Straße 3, 96050 Bamberg, Germany"

authornote: |
  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}

  \addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}

  The authors declare no competing financial interests.
  The code for this study is available at [https://osf.io/uksbc](https://osf.io/uksbc).

@@

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
---

@@

The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly avaible.
The stimuli and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).

>>>>

author: 
  - name          : "Alexander Enge"
    affiliation   : "1,2"
    corresponding : "yes"
    address       : "Rudower Chaussee 18, 12489 Berlin, Germany"
    email         : "alexander.enge@hu-berlin.de"
  - name          : "Franziska Süß"
    affiliation   : "3"
  - name          : "Rasha Abdel Rahman"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
  - id            : "2"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig"
  - id            : "3"
    institution   : "Fachhochschule des Mittelstands, Bamberg"

authornote: |
  Alexander Enge \orcidlink{0000-0003-0100-2297} [https://orcid.org/0000-0003-0100-2297](0000-0003-0100-2297)

  Rasha Abdel Rahman \orcidlink{0000-0002-8438-1570} [https://orcid.org/0000-0002-8438-1570](0000-0002-8438-1570)

  The authors declare no competing financial interests.
  The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).

@@

documentclass     : "apa6"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage{orcidlink}
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
---

@@

The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly avaible.
The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
